The function--sheaf dictionary for smooth commutative group schemes over finite fields, with applications over local fields

### 2014-08-22 dictionary.tex

Section~\ref{sec:disc-isog} focuses on the right-hand side of \eqref{eq:intro-snake},
giving descriptions of quasicharacter sheaves that are particularly useful when $G$ is connected.  In Section \ref{ssec:descentG}
we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$, and in Section \ref{ssec:discrete_isogenies}
those that arise via pushforward from a constant sheaf along a discrete isogeny $H \to G$.  When $G$ is connected,
we show in Section~\ref{} that every quasicharacter sheaf can be described in both of these ways.  We also show that $\TrFrob{G}$ is an isomorphism
in this case.

In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
and Weil restriction.
Sections~\ref{ssec:descentG} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
forming two important subcategories of $\QC(G)$.
%These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
In Section \ref{ssec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
of quasicharacter sheaves in this case.
In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
induces an essentially surjective functor of quasicharacter sheaves.
%Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
%is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
%to characters of $G(\Fq)$.

>>>>

Section~\ref{sec:disc-isog} focuses on the right-hand side of \eqref{eq:intro-snake},
giving descriptions of quasicharacter sheaves that are particularly useful when $G$ is connected.  In Section \ref{ssec:descentG}
we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$, and in Section \ref{ssec:discrete_isogenies}
those that arise via pushforward from a constant sheaf along a discrete isogeny $H \to G$.  When $G$ is connected,
we show in Section~\ref{ssec:connected} that every quasicharacter sheaf can be described in both of these ways.
We also show that $\TrFrob{G}$ is an isomorphism in this case.

In Section~\ref{sec:main} we prove that the rows of \eqref{eq:intro-snake} are exact and
use the snake lemma to determine the kernel and cokernel of $\TrFrob{G}$ for general $G$.
We show that $\QCiso{G^0} \to \QCiso{G}$ is surjective in Section~\ref{ssec:restriction} and
that the remainder of the top row of \eqref{eq:intro-snake} is exact in Section~\ref{ssec:component}.
We put it together in Theorem~\ref{thm:snake} of Section~\ref{ssec:snake}, showing that $\TrFrob{G}$
is surjective with kernel $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$.  Having described the isomorphism classes of objects,
in Theorem~\ref{thm:autornaught} of Section~\ref{ssec:qcmor} we show that
\[
\Aut(\qcs{L}) \cong \Hom(\pi_0(\bG)_{\Weil{}}, \EEx)
\]
and that every morphism is either trivial or an isomorphism.  We conclude in Section~\ref{sec:basechange} by
giving functorial versions of the restriction and norm homomorphisms $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
and describing how quasicharacter sheaves behave under Weil restriction.

Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from the earlier sections
to give a description of the categories of
